Hydra Battles and Cie

### 2021-08-14 doc/part-hydras.tex
Update doc/part-hydras.tex
Co-authored-by: Karl Palmskog <palmskog@gmail.com>

\index{Coq}{Unicity of equality proofs}

\label{sect:eq-proof-unicity}

@@

\input{movies/snippets/E0/LtDef}

@@

\index{hydras}{Exercises}
\begin{exercise}
In earlier versions of this development, the predicate \texttt{nf} was defined  inductively, with various constructors describing all possible cases.
\begin{enumerate}
\item Please give such a definition, in a dedicated module.
\item Prove the logical equivalence between your definition and ours.
\item Define a variant of the type \texttt{E0} (with your definition of \texttt{nf}).
\item Can you still prove a lemma like \texttt{E0\_eq\_iff} ? With the help of an axiom from some module of the standard library ?
\end{enumerate}
\end{exercise}

@@

\label{sect:omega-T1}
\input{movies/snippets/E0/ZeroOmega}

@@

\begin{Coqsrc}
Fixpoint succ (alpha:T1) : T1 :=
  match alpha with 
   | zero => 1
   | ocons zero n _ => ocons zero (S n) zero
   | ocons beta n gamma => ocons beta n (succ gamma)
 end.
\end{Coqsrc}
%
% TO do : insert succ in E0
%

>>>>

\index{Coq}{Unicity of equality proofs}
\label{sect:eq-proof-unicity}

@@

\input{movies/snippets/E0/LtLeDef}

@@

@@

\label{sect:omega-T1}

\input{movies/snippets/E0/ZeroOmega}

@@

\begin{Coqsrc}
Fixpoint succ (alpha:T1) : T1 :=
  match alpha with 
   | zero => 1
   | ocons zero n _ => ocons zero (S n) zero
   | ocons beta n gamma => ocons beta n (succ gamma)
 end.
\end{Coqsrc}
